% Pigs: Protocol-Native Phased Orchestration for LLM API Requests
% Full Conference Paper (English)

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, shapes.geometric, fit, backgrounds}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{natbib}

\lstdefinelanguage{Rust}{
  keywords={fn,let,mut,pub,struct,enum,impl,trait,use,mod,async,await,return,if,else,match,for,while,loop,break,continue,move,ref,self,Self,where,as,in,box,dyn,unsafe,extern,crate,const,static,type,true,false},
  sensitive=true,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
  morestring=[b]',
}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  language=Rust,
  keywordstyle=\color{blue!70!black},
  commentstyle=\color{green!50!black},
  stringstyle=\color{red!60!black},
}

\title{Pigs: Protocol-Native Phased Orchestration for LLM API Requests}
\author{Anonymous}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Large Language Model (LLM) agents typically interact with providers through stateless API calls, lacking built-in mechanisms for planning, execution verification, and failure recovery. While frameworks like ReAct and Reflexion add multi-stage reasoning within a single conversation, they rely on the LLM itself to manage control flow---an approach that is fragile, protocol-specific, and opaque to downstream tooling. We present \textbf{Pigs}, a phased orchestration middleware that wraps LLM API requests with a deterministic Pre$\rightarrow$Executor$\rightarrow$Post state machine using lightweight text control markers (\texttt{PIGEND}/\texttt{PIGFAIL}) for routing. Pigs preserves the complete protocol-native HTTP request---method, path, headers, and JSON body---across three API protocols (OpenAI Chat Completions, Anthropic Messages, OpenAI Responses), modifying only the model identifier, current user input, and phase transcript. Phase subrequests re-enter the local proxy via HTTP loopback, transparently inheriting channel selection, model mapping, body cleaning, and retry logic. External tool execution is supported through a bounded in-memory continuation store with TTL and capacity limits. We evaluate Pigs through four experiments: an ablation study isolating each phase's contribution, a control marker effectiveness study, a three-protocol consistency evaluation, and a cost-benefit analysis. \textbf{Experimental results are pending and will be filled upon completion of the evaluation.}
\end{abstract}

\input{sections/introduction}
\input{sections/background}
\input{sections/design}
\input{sections/implementation}
\input{sections/experiments}
\input{sections/results}
\input{sections/related}
\input{sections/discussion}
\input{sections/conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
